Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-06-05 paper.tex
Updated pdf

Figure~\label{AllData} shows values of solar wind averages and mass density used in this study.

We will briefly compare our results to other published results to verify our methods and handling of data.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage

>>>>

Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage
